### 2023-02-02 manuscript.tex
bioschemas in ceur [ci skip]
This build is based on
https://github.com/stain/2022-fdo-paper/commit/752f19bbb05f04e1d3a3cb2f18122c2e8ba953c7.

This commit was created by the following CI build and job:
https://github.com/stain/2022-fdo-paper/commit/752f19bbb05f04e1d3a3cb2f18122c2e8ba953c7/checks
https://github.com/stain/2022-fdo-paper/actions/runs/4076315629

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/1cbe9b42e4c7f0fecfd786fcff5fbd152fe3abdb/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/1cbe9b42e4c7f0fecfd786fcff5fbd152fe3abdb}{stain/2022-fdo-paper@1cbe9b4}
on February 2, 2023.

>>>>

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/752f19bbb05f04e1d3a3cb2f18122c2e8ba953c7/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/752f19bbb05f04e1d3a3cb2f18122c2e8ba953c7}{stain/2022-fdo-paper@752f19b}
on February 2, 2023.
